% Exemple de CV utilisant la classe moderncv
% Style classic en bleu
% Article complet : http://blog.madrzejewski.com/creer-cv-elegant-latex-moderncv/

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}                
\usepackage[utf8]{inputenc}
\usepackage[top=1.1cm, bottom=1.1cm, left=2cm, right=2cm]{geometry}
% Largeur de la colonne pour les dates
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{Timothy}
\familyname{Lim}
\title{}              


% \address{Flat 28 110 Kensington Park Road }{London UK, W112PJ}    
\email{timothy\_lim@outlook.com}                      
% \homepage{www.madrzejewski.com}
% \mobile{06 27 62 55 41} 
\homepage{www.timothylim.info}
\extrainfo{Github: timothyylim}
\begin{document}
\maketitle

\section{Education}
\cventry{2015 -- 2016}{Master of Science in Computing Science}{Imperial College}{London, United Kingdom}{}{Expected Graduation: October 2016.}
\cventry{2011 -- 2015}{Bachelor of Arts in Economics}{Brown University}{Providence, United States of America}{3.6/4.0}{Coursework: Micro and Macro Economics, Behavioural Economics, Econometrics, Intro to Object Oriented Programming, Algorithms and Data Structures.\newline{}Awards: Shelby Davis Scholarship.  }
\cventry{2009 -- 2011}{International Baccalaureate}{United World College of the Atlantic}{Wales, United Kingdom}{}{}

\section{Experience}
\cventry{September 2015\\-  Present}{Data Engineer}{PostoExpress}{Kuala Lumpur, Malaysia}{}{Leading the processing and analysis of data at a high-growth startup. Building out infrastructure and real-time
predictive models to drive insights as we scale.\newline{}}

\cventry{September 2014\\-  December 2014}{Computer Science Teaching Assistant}{Brown University}{Providence, United States of America}{}{Delivered projects used to teach a computer science course of 300 students. Led lab sessions of 20 undergraduates and assisted with office hours and exam grading throughout the semester.\newline{}}

\cventry{July 2014\\-  September 2014}{Group API Intern}{Axiata Digital Services}{Kuala Lumpur, Malaysia}{}{Developed and presented an Android tablet application that was featured in the Haffenreffer Museum of Anthropology.\newline{}}

\cventry{May 2012\\-  April 2012}{Labratory Assitant}{Center For Human Genetic Research, Massachusetts General Hospital}{Boston, United States of America}{}{Assisted with leading research into defining proteins that regulate tumor growth.\newline{}}



\section{Projects}
\cvitem{Haze Watch}{An open source project to provide localised air pollution readings for Malaysian cities via an automated twitter feed.}
\cvitem{NYC Subway Analysis}{A statistical analysis of ridership on the New York City Metro.The project is split into two notebooks, the first outlining exploration of the dataset and the second, the analysis.}

\section{Skills}
\cvitem{Languages}{English, Malay, Norwegian (conversational), Swedish (basic)}
\cvitem{Programming Languages}{
Fluent in: Java, C++, Python, SQL \newline{}
Familiar with: PHP, Javascript 
}

% \cvitem{Frameworks}{D3.js, Java Swing}
\cvitem{Statistical Packages}{Stata, R, SPSS, scipy}
% \cvlanguage{Anglais}{lu, écrit, parlé -- Toeic 965 / 990}{}


\section{Interests}
\cvitem{Literature}{Happy to talk about anything from Dune to Moby Dick.}
\cvitem{Football}{A reluctant lover of the beautiful game.}
% \cvitem{Entreprenariat}{Passive Income, The 4 hour work week}
%\cvitem{Plongée}{Diplôme de niveau 1}

\end{document}

% Source: http://blog.madrzejewski.com/creer-cv-elegant-latex-moderncv/